### 2014-04-14 doc/uist14/abstract.tex
a significant amount of new content and changes on papers

%!TEX root = uist14.tex
Emerging head-worn computing devices can enable hands-free interactions with smart objects in physical spaces. 
%
We introduce and characterize a method for selecting and interacting with physical targets at a distance using head orientation. We augment a commercial wearable device, Google Glass, with an infrared (IR) emitter to select targets equipped with IR receivers. A target acquisition study with 14 participants shows that selection using head orientation with our device outperforms list selection on a wearable device. The fundamental imprecision of head orientation requires disambiguation techniques when the intended target is unclear. To improve on the slow manual disambiguation of our first design, we introduce a second design in which receivers use IR intensity sensors to estimate which target is the intended selection. A second study demonstrates that using IR intensity successfully reduces ambiguity and enhances selection speed. Finally, we describe how a spatial data structure can be inferred to enable a natural mapping of head direction during the disambiguation step and we report first use data. 
We demonstrate an application of our selection technique for controlling smart appliances and report qualitative user impressions.

>>>>

%!TEX root = uist14.tex

\ben{This parts needs to be changed based on the current flow of the story.}
Emerging head-worn computing devices can enable hands-free interactions with smart objects in physical spaces. 
%
We introduce and characterize a method for selecting and interacting with physical targets at a distance using head orientation. We augment a commercial wearable device, Google Glass, with an infrared (IR) emitter to select targets equipped with IR receivers. We present our iterative design process that has shown with IR, it outperforms a pure list selection. And with IR intensity, the time can be further reduced. If head motion is added, we can infer a spatial data structure of the nodes to enable a natural head-motion based disambiguation.
We demonstrate an application of our selection technique for controlling smart appliances and report qualitative user impressions.

### 2014-04-14 doc/uist14/applications.tex
a significant amount of new content and changes on papers

\bjoern{since length will be an issue, let's just focus on glass remote and skip the others?}
Additional applications such as attention tracking or indoor position and orientation estimation of a wearer based on our technique are conceivable; we leave them to future work.

>>>>

\bjoern{since length will be an issue, let's just focus on glass remote and skip the others?}
\ben{I still think that by listing a few other applications, it helps identifying the importance of physical targeting. We may do that with a short paragraph instead of a subsection.}
Additional applications such as attention tracking or indoor position and orientation estimation of a wearer based on our technique are conceivable; we leave them to future work.

### 2014-04-14 doc/uist14/intro.tex
a significant amount of new content and changes on papers

\begin{figure}[t]
\centering
\includegraphics[width=1.0\columnwidth]{figures/teaser.jpg}
\caption{An example application of head-orientation targeting: Using an augmented head-worn device (1), users can control smart home appliances (2) by looking at them. A near-eye display then shows an appliance control UI (3), which users navigate through multitouch gestures.}
\label{fig:teaser}
\end{figure}

@@

In this paper, we describe the iterative development and evaluation of an area-selection technique that can be readily implemented with small hardware changes to emerging wearable devices. We augment Google Glass\footnote{\url{http://www.google.com/glass/start/}} to enable (IR) communication between Glass and target appliances. The cone shape of light emitted by an IR LED (a diameter of 60-120cm and distance up to 6m) provides the {\em coarse} selection area. To {\em refine} selection when multiple targets have received IR signals, we first introduce a manual technique where users select a candidate device using a graphical interface on their wearable device.  We then conduct a study with $14$ participants that compares acquisition times for physical targets in a room for our technique and an alternative list selection interface. We find that target acquisition through head orientation is preferred by users and is faster than list selection, given the constraints of linear input using a head-worn touch controller.

>>>>

@@

In this paper, we describe the iterative development and evaluation of an area-selection technique that can be readily implemented with small hardware changes to emerging wearable devices. We augment Google Glass\footnote{\url{http://www.google.com/glass/start/}} to enable infared (IR) communication between Glass and target appliances. The cone shape of light emitted by an IR LED (a diameter of 60-120cm and distance up to 6m) provides the {\em coarse} selection area. To {\em refine} selection when multiple targets have received IR signals, we first introduce a manual technique where users select a candidate device using a graphical interface on their wearable device.  We then conduct a study with $14$ participants that compares acquisition times for physical targets in a room for our technique and an alternative list selection interface. We find that target acquisition through head orientation is preferred by users and is faster than list selection, given the constraints of linear input using a head-worn touch controller.

### 2014-04-14 doc/uist14/iteration1.tex
a significant amount of new content and changes on papers

%!TEX root = uist14.tex
\section{Study 1: Physical Target Acquisition Study}
To understand the accuracy and performance of head-orientation-based selection through our device, we carried out a comparative target acquisition study, where participants had to connect to wireless nodes distributed in a room with our technique, and with an alternate list selection approach.

\subsection{Apparatus}
In an indoor environment, 10 wireless nodes are spread across a room (Figure~\ref{fig:targeting-study-layout}). Each node is an embedded wireless system with a microcontroller, IR receiver, a wireless XBee radio, and three status LEDs %(Figure~\ref{fig:target}). %An yellow LED indicates that the device is the target that should be selected in the current trial; a red LED lights up whenever the device receives an IR signal from Glass; a blue LED shows when participants have successfully connected to a device, and is also used for disambiguation when multiple targets are within IR range. 
Next to each target, a paper sheet shows a number and letter combination, which is used for uniquely identifying the device. The numbers are the primary identifiers, ordered from left to right in the room.

\begin{figure}[t]
\centering
\includegraphics[width=1.0\columnwidth]{figures/targeting-study-layout.pdf}
\caption{In the targeting study, participants had to find and select one of 10 targets in a lab environment. Targets were called out by number; for the list mode condition, participants need to match numbers to letters.}
\label{fig:targeting-study-layout}
\end{figure}
%\begin{figure}[b]
%\centering
%\includegraphics[width=0.8\columnwidth]{figures/study-node.pdf}
%\caption{An example node from the targeting study --- we constructed 10 such nodes - each mounted in a box.}
%\label{fig:target}
%\end{figure}

\subsection{Methodology}
In our within-subjects design, participants performed 15 target acquisition tasks each with two interaction styles. In the {\em infrared} mode condition, participants used our IR targeting approach; in the {\em list} mode condition, participants had to look up a device's letter code on the printed paper next to the device and then select that letter code from a list displayed on their Glass device. The list was navigated with swipe motions on the Glass touchpad. For each task, participants started at a fixed position in the room. The experimenter called out a number and simultaneously started a timer. Participants then had to find the corresponding device (by looking for its printed code). In the {\em infrared} mode, participants then selected and acquired the target by aiming the IR beam at the target, and confirmed their selection with a touch pad tap. If more than one target was within range, participants had to either use the disambiguation dialog or reposition themselves. In the {\em list} mode, participants had to read the letter next to the number and then select that letter by browsing a linear list shown in their Glass display. While the list was alphabetized, letter arrangement in the room was not. This design required participants to find the target in the room before starting a list navigation to keep visual search times similar in each condition.

Afterwards, participants completed a survey that elicited answers to Likert-scale questions as well as open-ended answers about their experience.

\subsection{Participants}
We recruited 14 participants from our institution. 13 had never used Glass before. 4 wore prescription glasses, which may have affected their task performance as wearing glasses beneath Glass makes it more cumbersome to secure the position of Glass and to adjust the screen to the optimal angle. Half of them performed {\em infrared} mode first and the other half did {\em list} mode first.

\subsection{Measures}
The main measures were {\bf target acquisition time}: the time required to identify, select, and connect to a wireless target device; and {\bf user preference}: which interface users preferred for the task after completing the study.

\subsection{Results}
\subsubsection{Performance data}
The time to complete each task can be broken down into the following pieces:

$t_{infrared}=t_{locate}[+t_{reorient}][+t_{disambiguate}]+t_{tap}$

$t_{list}=t_{locate}+t_{listnav}+t_{tap}$

In both conditions, participants first have to locate the target announced by the experimenter through visual search ($t_{locate}$). In the {\em infrared} mode, participants may then directly confirm their selection if only a single target was selected ($t_{tap}$). However, if they don't immediately receive feedback that their target was selected, or if multiple targets were selected, users either have change their position or head orientation ($t_{reorient}$) or they have to step through the on-screen disambiguation dialog ($t_{disambiguate}$). In the {\em list} mode, participants must scroll through the list to find the desired target identifier ($t_{listnav}$).
Thus, {\em infrared} will show a performance benefit if $(t_{reorient}+t_{disambiguate})<t_{listnav}$. This depends on the number of total devices in the environment (increasing $t_{listnav}$), and their density (which will increase $t_{disambiguate}$).

\begin{figure}[t]
\centering
\includegraphics[width=1.0\columnwidth]{figures/R_time_by_Category.pdf}
\caption{Boxplot of task completion times for the comparison between {\em infrared} mode and {\em list} mode (A), and between IR multiple responses cases and IR single response cases (B). The centers of boxes are median values, while white dashed lines are mean values.}
\label{fig:selection-times}
\end{figure}

We first show results for 10 targets and then discuss extrapolations of these results. Average target acquisition time $t_{infrared}$ was 6.67 seconds, while $t_{list}$ was 8.86 seconds (Figure~\ref{fig:selection-times}A). This difference is significant (Student's t-test, $t(279)=-3.81, p=0.00017$). % \bjoern{you need to report the t statistic and degrees of freedom as well - t(df)= n,p=m.}

To further understand the performance gain in {\em infrared} mode, especially the factor $t_{disambiguate}$, we compare selection times when multiple devices are targeted (and disambiguation is required) to single-device selection times (Figure~\ref{fig:selection-times}B). When there is a single device, $t_{disambiguate}$ is 0 and it takes 6.40 seconds (on average) to complete the connection. When multiple devices are in range, the time increases to 9.16 seconds, indicating 2.76 seconds required to disambiguate. Though it takes significantly longer ($t(19)=-2.7827, p=0.012$ using t-test) in the {\em multiple} case, these cases made up only 10\% of total infrared trials.
%, even we intentionally placed a few devices nearer to each other. % 19 / (19+168 )

@@

For each device, $t_{listnav}$ depends on their relative position in the list. Figure~\ref{fig:time-vs-list-order} shows the time it takes to select a device (means and standard deviations) as a function of its list position - the trend line (dotted) enables extrapolation to estimate at what number of devices the {\em infrared} mode interaction techniques will outperform {\em list} mode\footnote{The higher mean value at $order=1$ is caused by one outlier when the participant tried multiple times in {\em list} mode to connect to the right target.}. From the figure, we can see that once the target's order has increased to be larger than 6, the average $t_{listnav}$ for that target would be larger than $t_{reorient} + t_{disambiguate}$. We expect that, when the number of targets keeps increasing, there would be larger time reduction in {\em infrared} mode.

% \bjoern{A linear trend is visible, and the regression returns with coefficient of determination ($R^2=0.032$). --- This R value is basically no correlation at all! try to run a correlation only on the median times. }

Participants' selection errors do occur in both conditions. However, error rates were low (1.1\% in {\em infrared} mode, and 2.9\% in {\em list} mode, respectively). This precludes us from running a more detailed analysis.

%\subsubsection{Preference}

@@

>>>>

%!TEX root = uist14.tex

\section{Iteration 1: IR vs. List}
Our system design uses IR as the beam cursor for physical target selection because the area coarse selection will remove the targets outside of users' view range. And this could help during the fine selection time because there is a smaller set of targets for fine selection. The opposite is to have a complete list of all targets when there is no single coarse selection and the disambiguation is always needed. This brought up the first question that we asked ourselves -- {\em how much does using IR help in reducing the selection time}. To answer that question and quantify the benefit of having IR for the coarse selection, we carried out our first target acquisition study which compares the {\em IR selection} and {\em list selection}.

We deployed 10 wireless nodes in an indoor environment (Figure~\ref{fig:targeting-study-layout}). Each of them has a number as ID and a letter representing the name. There are 14 participants from our institution for this study. 13 had never used Glass before, therefore we offered a Google Glass crash course before the experiment for them to get familiar with Glass gestures. 4 of them wore prescription glasses, which may have affected their task performance as wearing glasses beneath Glass makes it more cumbersome to secure the position of Glass and to adjust the screen to the optimal angle.

\begin{figure}[t]
\centering
\includegraphics[width=1.0\columnwidth]{figures/targeting-study-layout.pdf}
\caption{In the targeting study, participants had to find and select one of 10 targets in a lab environment. Targets were called out by number; for the list mode condition, participants need to match numbers to letters.}
\label{fig:targeting-study-layout}
\end{figure}

In the within-subject study, half of them performed {\em IR selection} first and the other half did {\em list selection} first. For each selection condition, we conducted 15 target selection by random choosing from all the targets. During the study, we measure the {\bf target acquisition time} for each target selection, and afterwards, participants were asked to complete a survey that elicited answers to Likert-scale questions as well as open-ended answers about their experience.

%% remove this for now
%% Our measurements suggest that IR communication can be targeted to an area about 60-120cm in diameter, up to 5m in front of the user. These values are a reasonable match for selecting targets in a room-size environment. A wider beam would lead to an increased chance of multiple appliances receiving IR signals simultaneously. A narrower beam will make targeting more challenging, given the precision constraints of human head movement.

\begin{figure}[t]
\centering
\includegraphics[width=1.0\columnwidth]{figures/R_time_by_Category.pdf}
\caption{Boxplot of task completion times for the comparison between {\em infrared} mode and {\em list} mode (A), and between IR multiple responses cases and IR single response cases (B). The centers of boxes are median values, while white dashed lines are mean values.}
\label{fig:selection-time}
\end{figure}

Our results indicate that {\em IR selection} is generally better than {\em list selection}. From Figure~\ref{fig:selection-time}A, the average target acquisition time for {\em IR selection} is 6.67 seconds, while for {\em list selection} it took 8.86 seconds. We run Student's t-test on the data and it shows significant difference ($t(279)=-3.81, p=0.00017$).

To further understand if the gain comes from the coarse selection, we splited the data from {\em IR selection} to two parts -- ones that require disambiguation and ones that don't. The result is shown in Figure~\ref{fig:selection-time}A. It shows that it takes 6.40 seconds (on average) to complete the connection if coarse selection has achieved the acquisition, while when multiple devices are in range, the time increases to 9.16 seconds, indicating additional 2.76 seconds for disambiguation. Though it takes significantly longer ($t(19)=-2.7827, p=0.012$ using t-test) in the latter case, they only happen 10\% of total {\em IR selection} trials.

From the above result, we learned that with IR, we can have effectively reduced the overall target acquisition time. And the major gain comes from the fact that {\em coarse selection} helps reduce the chances of entering {\em fine selection} stage.

@@

To further generalize the results, in Figure~\ref{fig:time-vs-list-order}, we show the acquisition time for each individual target in {\em list selection} condition, ordered by their relative position in the list. Since with IR technique, the acquisition time is invariant from each target's order, we use solid lines to represent the average performance of {\em IR selection}. From this figure, we can see that once the target's order is larger than 6, the average acquistion time will be larger than the case when disambiguation is needed in {\em IR selection}. Therefore, we argue that once there are more targets in the physical space, the {\em list selection} is not scalable.

\ben{qualitative feedback hasn't been added yet for this part.}
%\subsubsection{Preference}

@@

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "uist14"
%%% End:

### 2014-04-14 doc/uist14/system.tex
added a figure
structural layout as discussed on sunday - iterative development
a significant amount of new content and changes on papers

\section{System Design and Prototyping}
\label{sec:syst-design-prot}

This section describes the design and implementation of our prototype system. We start by summarizing the design considerations in this head-orientation targeting, and for each consideration, we make the choice of commercial off-the-shelf (COTS) components. Afterwards, we conclude this section by a depiction of the overall system architecture that is used for both our study and future application development.

\subsection{Design Considerations}
\label{sec:design-cons}

To effectively enables the physical targeting based on user's head movement, and build such a platform for applications, we have come up with the following design considerations and the justification for each.

{\bf Directional area selection:} To be aligned with the user's head orientation, the sensing modality should be directional. Merely direction is not enough, from Section~\ref{sec:background}, the head muscle's fundamental limitation and Fitts' law imposes us to choose an area selection technique. However,  with a larger coverage area, there will be a higher chance for disambiguation. We should find the proper technique that achieves area selection while still providing ways for a more fine-grained resolution.

% the two visual feedback seems a bit random...
{\bf Leverage visual feedback:} Since the user cannot see his own head orientation, there should be some effective ways to provide feedback to the users. We consider two types of visual feedbacks. The first comes from the environment which enables instantaneous visual cue while the user is looking around. The second should remain unchanged even if the users' head orientation has changed; in such a way, further interactions are enabled without imposing the burden of staring. But such a display shouldn't distract the user's current line-of-sight attention -- which means a near-eye display is better than using a hand-held device.

% A calmer~\cite{weiser_coming_1997} approach is to locate visual feedback about selection targets in the environment, to prevent distraction and interruption. Such feedback should be delivered instantaneously, while users look around a room.

{\bf Flexible communication:} The system is for the interaction with the environment, therefore the communication among devices should be flexible. Especially there would be a consensus problem if the end-nodes are not agreeing on what the user is looking at. The communication would be necessary for resolving the inconsistency in such a distributed environment. Also providing a flexible communication capability can make the system as a platform for other applications.

{\bf Adjustable angle:} From our pilot study, we have learned that human's head orientation pointing is biased for each person. In order to align area selection technique, there should be ways to adjust or calibrate the covered area.

These design considerations find their expression in our selection of techniques in the following few subsections.

\subsection{IR as beam cursor}
\label{sec:ir-as-beam}

For the directional area selection technique, we have chosen to use infrared (IR) for a couple of reasons.

First, the signal characteristics of IR makes it suitable for directional area selection. There are a wide range of viewing angles that we can choose (DigiKey offers IR emitters from $4^\circ$ to $240^\circ$, however, most are around $20^\circ$ of viewing angle). This leads to a cone shape-like area coverage and can be well-aligned with humna's line of sight.

Second, for the disambiguation consideration, since the infrared illuminance falls off with respect to both the offset angle from the center and the distance to the emitter, even though the signal might cover multiple targets, using the intensity from the receivers can help disambiguation.  
% for the 4 degree to 240 degree, I used information from http://www.digikey.com/product-search/en/optoelectronics/infrared-uv-visible-emitters/524328?k=IR

In addition, IR has been used for remote control for many years. The emitters and receivers are fairly cheap to manufacture; and it's easy for integration with existing devices. 
What's more, IR is immune to most interference sources. The ambient IR might influence the IR receivers' intensity reading, however with simple IR signal validation, the receiver is still safe. There might be issues for signal reflection, either bouncing from the ground to the target or bouncing back to the opposite direction. However, such visual feedback is not aligned with the user's attention so no further action from the user might be taken; or the genuine target could easily beat the false positive since the one with reflection tends to travel a longer distance, making the signal strength smaller.

Therefore, we can attach an IR emitter to capture the head orientation and install some IR receivers in the environment for both signals detection and intensity reading. For our prototype, we have found some COTS components for IR. 
The IR emitter is the one from OSRAM Opto Semiconductors Inc with manufacturer part number SFH 4545. From the datasheet, it has a view angle of $10^\circ$. Part of the reason we have chosen it is because the radiant intensity can quite high if we provide it with sufficient current flow (550mW/sr @ 100mA). We can then easily adjust it using a resistor to satisfy different demands. 
% transmitter webpage: http://www.digikey.com/product-search/en?x=0&y=0&lang=en&site=us&KeyWords=475-2919-ND
For the IR receiver, we use 38.0kHz IR Receiver Modules from Vishay Semiconductor Opto Division (manufacturer part number TSOP38238). 
% receiver webpage http://www.digikey.com/product-detail/en/TSOP38238/751-1227-ND/1681362
In order to read the IR intensity, we integrates another IR light-to-voltage converter from AMS-TAOS USA Inc (manufacturer part number TSL267-LF) which is pretty sensitive to IR irradiance. 
% http://www.digikey.com/product-detail/en/TSL267-LF/TSL267-LF-ND/3095052

We use Arduino platform for the prototyping, and there is an easy-to-use IR library\footnote{\url{https://github.com/shirriff/Arduino-IRremote}} where we can customize the IR signal for both transmission and reception. To read the IR intensity, an 10-bit ADC is attached to the output of TSL267-LF which gives a reading from 0 to 1023.

\subsection{Environment LEDs and Head-up display}
\label{sec:head-up-display}
As we have argued for the visual feedback design considerations, the environment should provide instantaneous visual cue to respond to user's head orientation. This can be easily achieved with 1-bit LEDs on each devices that has an IR receiver. For the visual feedback that is persistent even when the user's head orientation has changed, we have considered a few COTS solutions that support the head-up display, and ended up with Google Glass because it's easy to program (it supports standard Android programming) and the device is also light-weight for everyday use. At the time of writing, we have Google Glass running Android 4.0.4 (software version: XE12).

\subsection{Wireless Communication}
\label{sec:wirel-comm}

There are many choices of wireless communication techniques that we could consider to accompany IR's directional targeting. WiFi, Bluetooth Low Energy (BLE) and 802.15.4 (ZigBee) radio are all candidates for such communications. A detailed comparison is out of the scope of this paper. For our prototype, we have chosen to use XBee ZB\footnote{XBee: http://www.digi.com/xbee/}(based on ZigBee protocol and 802.15.4 radio) for the mesh network because of the ease to program and integration to Arduino platform. The COTS adapter provides an easy-to-use interface where we could use either hardware serial pins or the software serial library to send and receive messages.

As we mentioned that the communication capability has to be included to resolve the consensus view of head orientation, we use the star topology -- the node which controls IR emission acts as the PAN coordinator. It collects the IR received signal strength (RSS) from each targets and runs a local algorithm to determine which one is the current target.

Using such an architecture for communication also makes the integration with Google Glass easier. For now, Google Glass is capable of WiFi and Bluetooth; so we have added a Bluetooth modem to establish connections with Google Glass. We use BlueSMiRF Silver (WRL-12577) for our prototype.

\subsection{3D Printed Adjustable Holder}
\label{sec:3d-print-adjust}
To compensate for the bias of each person's line of sight with the IR emitter, we have designed the holder that can be easily attached onto Google Glass while we can adjust the beam angle flexibly.

\begin{figure}[t]
\centering
\includegraphics[width=0.9\columnwidth]{figures/placeholder.pdf}
\caption{we should replace this placeholder with Claire's design and printed version.}
\label{fig:3d-holder}
\end{figure}

\subsection{Overall System}
\label{sec:overall-system}
So far, we have described our choice separately, in this subsection we focus on our system architecture that stitches the components together. 
Figure 2 is our overall architecture photo. Because we need to take command from Google Glass, we have used another microcontroller that speaks Bluetooth to communicate with the Google Glass.

%% show the figure here

>>>>

\section{System Design}
We first present our system architecture and then dive into each component to justify our design choices.

\begin{figure}[t]
\centering
\includegraphics[width=0.9\columnwidth]{figures/architecture.pdf}
\caption{In our system architecture, targeting is captured by IR signal but the confirmation is over 802.15.4 radio. In the research prototype, users have to carry an additional microcontroller board that marshals messages between Google Glass' Bluetooth radio and the IR/802.15.4 interface. But our customized hardware can be also integrated into the wearable device.}
\label{fig:architecture}
\end{figure}

%% IR is a proper choice.
{\bf Area Beam Cursor:} To achieve area selection, our design focuses on using IR signals to detect the general head orientation in physical space. Each selectable target is equipped with IR receivers. We choose IR for a couple of reasons:
\begin{itemize}
\item The signal characteristics of IR makes it suitable for directional area selection. In general, IR covers a viewing angle of $20^\circ$ of viewing angle (though a wider range is avaialble in the market). This leads to a cone shape-like area coverage and can be well-aligned with users' line of sight. 
\item IR has been extensively used for remote control. The emitters and receivers are cheap to manufacture and easy to integrate.
\end{itemize}

%% We have chosen to use Google Glass.
{\bf Head-worn Computing Device:} We use Google Glass among the available COTS head-worn devices because it's easy to program (Android platform) and also light-weight for everyday use.

%% the following is commented out because it's hard to have it while we describe the iterative design procedure
%% We are interested in sensing two things: 1) IR communication and 2) IR intensity. Common IR receivers have automatic gain control built in and hide received signal strength. We therefore add an IR intensity sensor. In a commercial application, a single sensor that both decodes and reports RSSI could be designed.

{\bf Wireless communication:} Though there is a wide range of radios available for wireless communication, we made the choice of 802.15.4 and ZigBee protocol because it is specifically for mesh network and the nice integration with Arduino platform. However, for now Google Glass only supports WiFi and Bluetooth. We have to add a Bluetooth modem to bridge Glass and the rest of the system. \footnote{This is a compromise now, and we are planning to migrate the entire system to Bluetooth Low Energy (BLE) once Google upgrades the Glass software to Android 4.4+. The prototype now suffice our demand to study head orientation-based target selection.}

{\bf Visual Feedback from the environment:} Each target is equipped with multiple LEDs and these LEDs are used for visual feedback during the target selection process.

\ben{discussion on the choices of each}.
This architecture was chosen for reasons of expediency and we do not claim optimality for our design decisions. Future head-mounted devices could clearly integrate IR emitters; the choice of local wireless technology could also change. In particular, one could substitute WiFi modules or design an all-Bluetooth network.
